Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-20 Thesis/chapter/05-computational-details.tex
comp details ML

\iffalse 
\subsection{Fitting via Machine Learning}
\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
Python and sci-kit learn \td{cite} was used to implement a linear fit model, and SVR with the kernels polynomial, rbf and sigmoid. 
The space of hyper parameters C, the degree (in case of polynomial), epsilon and gamma was scaned.

The independent variables are located on a partially irregular grid.  
\fi

>>>>

\subsection{Fitting via Machine Learning}
%\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
Python and sci-kit learn \cite{pedregosa2011scikit} was used to implement a linear fit model, \gls{krr} and \gls{svm} with the kernels polynomial, \gls{rbf} and sigmoid. 
%\subsubsection{Grid Search}
A grid search over a set of hyper parameters was executed. 
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
% KRR 
The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid and polynomial with degree 1--4.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
% SVM
The kernels for \gls{svm} were the same as for \gls{krr}. 
Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$, 
where $C$ took the values 0.05--0.95 with 0.05 steps, $\varepsilon$ 0.02--3.8 with 0.2 steps 
and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
% GRID SEARCH 
The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
of the \gls{emma} data set were scaled before each calculation.
For each calculation the \td{5-fold} cross validation score was calculated. 
For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 
the parameters with the highest score were noted.
% 
Finally, the different data sets were predicted for each model and \gls{mae} and \gls{mse} were calculated.
These values were also calculated for \gls{emma} and the linear model in order to compare the different methods.

### 2023-02-20 Thesis/chapter/062-post-emma.tex
comp details ML

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Grid Search}
The ideal hyper parameters have to be found for \gls{krr} and \gls{svm}.
To do so a grid search over a set of hyper parameters was executed. 
Both \gls{krr} and \gls{svm} following kernel: radial basis function, sigmoid, and polynomial with degree 1 to 4. 
%
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
%
\td{which parameters?}
The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid and polynomial with degree 1--4.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
The kernels for \gls{svm} were the same and further hyper parameters were 
$C$, $\varepsilon$ and $\gamma_{ml}$, where $C$ took the values 0.05--0.95 with 0.05 steps, $\varepsilon$ 0.02--3.8 with 0.2 steps and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
%
\td{how and what?}
Each grid search calculation was calculated with and without scaling the data before the optimisation. 
For each optimisation \gls{mae}, \gls{mse}, $sigma(\mathbf{y})$ and $\sigma(\mathbf{\hat{y}})$ were calculated. 
For each method (\gls{krr} and \gls{svm}) and each kernel the parameters with the lowest \gls{mae} were chosen. 
%
\td{what were best results/hyper parameters}

@@

\begin{table}[htb]
	\centering
    \caption{Post EMMA vergleich}
	\label{tab:post-emma}
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    G&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
    \hline\hline
	\end{tabular}
    %
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    p&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        lin Reg&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
    \hline\hline
	\end{tabular}
\end{table}

@@

>>>>

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Grid Search}
\todo{reduce to results}
The ideal hyper parameters have to be found for \gls{krr} and \gls{svm}.
To do so a grid search over a set of hyper parameters was executed. 
Both \gls{krr} and \gls{svm} following kernel: radial basis function, sigmoid, and polynomial with degree 1 to 4. 
%
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
%
\td{which parameters?}
The parameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid and polynomial with degree 1--4.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
The kernels for \gls{svm} were the same and further hyper parameters were 
$C$, $\varepsilon$ and $\gamma_{ml}$, where $C$ took the values 0.05--0.95 with 0.05 steps, $\varepsilon$ 0.02--3.8 with 0.2 steps and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
%
\td{how and what?}
Each grid search calculation was calculated with and without scaling the data before the optimisation. 
For each optimisation \gls{mae}, \gls{mse}, $sigma(\mathbf{y})$ and $\sigma(\mathbf{\hat{y}})$ were calculated. 
For each method (\gls{krr} and \gls{svm}) and each kernel the parameters with the lowest \gls{mae} were chosen. 
%
\td{what were best results/hyper parameters}
\td{procedure into diffferen capitel: choose hyperparaters, choose dataset (emma). Grid search over hyperparameters and score with default scorer with default cross validation settings, k-fold=5? chose lowest score for each optimizand and algo (svm/krr) combo. Fit model with emma-data and chosen hyper parameters, predict different data sets and calculate statistics (MAE+MSE) for each data set.}

@@

\begin{table}[htb]
	\centering
    \caption{Post EMMA vergleich}
	\label{tab:post-emma}
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    G&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
%        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
    \hline\hline
	\end{tabular}
    %
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    p&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        lin Reg&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
%        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
%        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
        SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
    \hline\hline
	\end{tabular}
\end{table}

@@

\begin{verbatim}
(int.venv) [pur@lithium 2022]$ ./01_show_best.sh
cv_krr.g.scale.emma     -0.497302       0.252231        poly    deg=1   a=2.00  g=0.01  71/500
cv_krr.p.scale.emma     -0.449674       0.517822        rbf     deg=0   a=10.00 g=0.2   395/500
cv_svm.g.scale.emma     -0.368196       0.391125        poly    deg=2   C=0.7   e=1.0   g=0.5   7475/22000
cv_svm.p.scale.emma     -0.948249       0.439029        poly    deg=3   C=0.1   e=0.1   g=0.01  8801/22000
(int.venv) [pur@lithium 2022]$ ./3_calc_mse_of_best.sh -l
krr g poly -d 1 a10.00 g0.01    &17.37 &548.36 &30.42 &1477.36 &34.78 &2167.38 &22.75 &931.00\\
krr p rbf a2.00 g0.01   &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
svm g poly -d 1 C0.7 e0.1 -g0.01        &14.55 &415.40 &25.68 &1049.23 &28.49 &1587.85 &19.13 &676.39\\
svm p poly -d 1 C0.1 e0.1 -gscale       &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
\end{verbatim}

### 2023-02-20 Thesis/chapter/063-discussion.tex
comp details ML

\subsection{Discussion}
\subsubsection{Mistakes and Solutions}
%This chapter is structured as a letter 
%which my present self thinks that would have helped my past self 
%if recieved before the start of the practical part of my master practikum:\\

%to discuss: results from EMMA or rather which the data present are counter intuitive. 
%why lowest conductivity with lowest TCal and why is there a minimum for layers? 
%low TDOC results in lower conductivity... okay 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{ad results}
why correlation $\gamma$?

@@

\subsubsection{tips for next time}

@@

    \item \textbf{planning} gives chance of zooming out, force oneself to get an overview and to decide how much time on each task
    \item \textbf{research} phase is most important, dig into basics, discuss ideas with colleagues or go into detail about plan. Understand details of methods. Make a dummy run. Collect (dis-)advantages of different methods. Like in design project: do as many and as deverse solutions as possbile. Compare and combine the best parts. Reading will let learn from others mistakes. \\ \td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, could have been verhindert durch lesen the docu and more papers more thoughoughly. Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}

@@

	\item State the problem 
	\item Formulate the hypothesis
	\item Design the experiment/generate the data
	\item Collect the data and perform preprocessing
	\item Estimate the model 
	\item Interpret the model/draw the conclusions

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsectoin{discussion}
\begin{itemize}
    \item regularization
    \item reproducability (random in code and repeat sample)
    \item error of a sample 
\end{itemize}

>>>>

\subsection{Discussion}
\subsubsection{Mistakes and Solutions}
%why lowest conductivity with lowest TCal and why is there a minimum for layers? 
%low TDOC results in lower conductivity... okay somehow 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{ad results}
\begin{itemize}
    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
\end{itemize}

@@

\subsubsection{Tips for next time}

@@

    \item \textbf{planning} gives chance of zooming out and force oneself to get an overview and to decide how much time on each task
    \item \textbf{research} phase is most important, dig into basics, discuss ideas with colleagues or go into detail about plan. Understand details of methods. Make a dummy run. Collect (dis-)advantages of different methods. Like in design project: do as many and as diverse solutions as possbile. Compare and combine the best parts. Reading will let learn from others mistakes. \\ \td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, could have been verhindert durch lesen the docu and more papers more thoughoughly. Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}

@@

    \item \textbf{State the problem}
    \item \textbf{Formulate the hypothesi}
    \item \textbf{Design the experiment/generate the dat}
    \item \textbf{Collect the data and perform preprocessin}
    \item \textbf{Estimate the model}
    \item \textbf{Interpret the model/draw the conclusion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{discussion}
\begin{itemize}
    \item regularization
    \item reproducability (random in code and repeat sample)
    \item error of a sample 
\end{itemize}
